\section*{PREFACE}
\thispagestyle{empty}

In the digital era, the rapid growth of visual data and multimedia content has created an increasing demand for efficient image compression techniques. Traditional compression standards are widely used, but they often struggle to maintain high perceptual quality at very low bitrates. As a result, learned image compression has emerged as a promising approach because it can optimize compression and reconstruction directly from data.

Among learned image compression methods, Generative Adversarial Network (GAN)-based models have shown strong potential for preserving perceptual quality, especially in low-bitrate scenarios. High-Fidelity Image Compression (HiFiC) is a representative framework that applies adversarial learning to improve the visual fidelity of reconstructed images. However, the high computational complexity of GAN-based models creates significant challenges for real-time and embedded deployment.

This thesis investigates a hardware--software co-design approach for accelerating learned image compression based on a quantized HiFiC GAN model. By combining the parallel processing capability of FPGA hardware with flexible software control, the proposed system aims to balance performance, hardware resource usage, and reconstruction quality. This work provides a practical foundation for deploying advanced learned image compression models in real-world systems.

We would like to express our sincere gratitude to Assoc. Prof. Nguyen Duc Minh and Dr. Hoang Phuong Chi for their guidance, support, and valuable feedback throughout the development of this thesis. We also thank the lecturers, researchers, and members of the EDABK laboratory at the School of Electrical and Electronics Engineering, Hanoi University of Science and Technology, for their assistance during system implementation and testing.

Due to limitations in time and experience, this thesis may still contain shortcomings. We welcome feedback from lecturers, reviewers, and colleagues so that this work can be improved in future development.

\cleardoublepage